\section{ADInstanceAPI}
\label{api:ad-instance-api}

\subsection{Interface Identity}

\npar \interface{ADInstanceAPI} provides methods to run the anomaly detection
algorithms for a given measurement or alarm trame, encapsulated in a ADCommand,
on an ADInstance.

\subsection{\method{execute(ADCommand, Callback)}}

\subsubsection{Resources Provided}

\begin{quote}
	\begin{description}
		\item[Syntax] \ 
		\begin{verbatim}
void execute(ADCommand command, Callback callback) 
    throws NullPointerException;
		\end{verbatim}
		\item[Arguments] \
		\begin{itemize}
			\item command: represents a request to run the anomaly detection algorithms
			for a given trame that is encapsulated in the command.
			\item callback: a communication channel back to the issuer to be able to
			return the results.
		\end{itemize}
		\item[Effect] The trame is analyzed. If historical measurement or alarm data
		is needed, it is fetched. The result is returned to the issuer in a callback.
		\item[Restrictions] \ 
		\begin{itemize}
			\item The given command is not null.
		\end{itemize}
	\end{description} 
\end{quote}

\subsubsection{Data Types Definition}

\begin{quote}
	\begin{description}
		\item[ADCommand] This object wraps a request to perform anomaly detection for
		the device that sent the trame.	
		\item[Callback] A mechanism to return results after an asynchronous call. 
	\end{description} 
\end{quote}

\subsubsection{Exception Definition}

\begin{quote}
	\begin{description}
		\item[NullPointerException] This exception is thrown if the command is null.
	\end{description} 
\end{quote}