\section{BillingSendAPI}
\label{api:other-billing-send-api}

\subsection{Interface Identity}

\npar \interface{BillingSendAPI} provides methods to send an invoice.

\subsection{\method{send(Invoice)}}

\subsubsection{Resources Provided}

\begin{quote}
	\begin{description}
		\item[Syntax] \ 
		\begin{verbatim}
void send(Invoice invoice)
    throws NullPointerException, IllegalInvoiceException,
    BillingServiceUnavailableException;
		\end{verbatim}
		\item[Arguments] \
		\begin{itemize}
			\item invoice: contains a consumed amount of a certain customer together with
			the owed payment. Additional information regarding the payment method is
			also included.
		\end{itemize}
		\item[Effect] The invoice is sent towards the customer included in the
		invoice.
		\item[Restrictions] \ 
		\begin{itemize}
			\item The given invoice is not null.
			\item The invoice contains customer information about where to sent the
			invoice to.
			\item The third party billing service is available (i.e. the network the
			billing service itself are up and running).
		\end{itemize}
	\end{description} 
\end{quote}

\subsubsection{Data Types Definition}

\begin{quote}
	\begin{description}
		\item[Invoice] This object contains all the necessary information for the
		customer to gain insight in the consumed amount and to be able to pay the
		invoice. 
	\end{description} 
\end{quote}

\subsubsection{Exception Definition}

\begin{quote}
	\begin{description}
		\item[NullPointerException] This exception is thrown if the given parameter is
		null.
		\item[IllegalInvoiceException] This exception is thrown when one or more of
		the crucial attributes of the Invoice are not present. This includes
		information to pay for the invoice or information to send the invoice.
		\item[BillingServiceUnavailableException] This exception is thrown when the
		third party billing service or the network is unavailable.
	\end{description} 
\end{quote}
