\section{Eliciting threats}
\label{sec:eliciting-threats}

\subsection{Assumptions}
\label{sec:assumptions}

\npar This sections includes all general and specific assumptions made to
influence the elicitation process.

\begin{enumerate}

  %General
  \item Non-compliance will be modelled as a single threat because it poses a
  threat to the whole system rather than to individual \textsc{dfd} elements.
  \item Non-repudiation does not form a threat to the system. In fact, it is a
  desirable aspect of the system. With no non-repudiation it is for
  example possible for a client to deny that he consumed the measured amounts
  of the different utilities.
  \item For datastores, dataflows and processes, detectability is not taken into
  account as a privacy threat. It is only important that the data itself is not
  leaked instead of the metadata. The core business of ReMeS after all involves
  measurements, modules, etc. Knowing that this information is present in the
  system is no big deal.
  \item The databases have weak access control since insiders can easily read
  the databases.
  \item Misactors have access to strong data mining techniques, since
  there is an enormous supply of optimized machine learing libraries available
  on the Internet.
  \item Side channel attacks are not considered to occur since they take a lot
  of analysis and the extracted information is not in correspondence of the
  effort.
   
  %Data stores
  \item All internal data stores are kept separate even though they are the
  possible target of the same threats (as seen in table
  \ref{table:threat-map-reduced}). This is done to stress the fact that the
  different databases could be linked together and is shown in a separate
  misuse case (T02).
  \item Linkability is a threat to the data stores because for example a
  researcher with malicious intents could link several data and commercialise
  this information.
  \item Identifiability forms a threat for data stores as well because it is
  impossible to omit all identification details out of the data. 
  \item Information disclosure for data stores is a logical threat because they
  contain all the data and this data needs to be protected at all times.
  \item Datastores are sufficiently protected so extra-monitor access and
  bad-storage management are not possible.
  
  % data flows
  \item All internal dataflows (i.e. dataflows between two internal processes
  and dataflows between an internal process and an internal data store) are only
  susceptible to insider threats, as we consider the back-end sufficiently
  protected against outsider threats. All these dataflows will therefore be
  combined into a single dataflow and only this dataflow will be examined.
  \item All bidirectional flows are combined into a single flow as there is no
  difference between the two directions . For example Consumer Portal - Consumer
  and Consumer - Consumer Portal are combined into Consumer Portal - Consumer.
  \item All portal - entity dataflows are combined into a single flow because
  there is no big difference between them regarding privacy.
  \item Detectability and information disclosure are not considered as a threat
  for external dataflows (i.e. flows between an entity and a process) as we
  assume that those flows are encrypted (e.g. with the SSL protocol). Internal
  dataflows, however, are not necessarily encrypted and are still vulnerable to
  information disclosure.
  \item Because the flows are assumed to be encrypted, all external entities
  will need to be able to execute these encryption algorithms themselves. This
  might form a problem for remote modules as their resources are limited.
  However, there are two reasons why this will not cause problems. First of all
  the modules can run leak detection algorithms so running the encryption
  algorithms in addition to the leak detection ones will not cause performance
  issues. Second, modules which communicate through WiFi need this encryption
  functionality anyway to communicate.
  \item It is possible that there is information disclosure on the Outgoing
  Communication Component - Consumer dataflow when the alarm recipients are
  wrong (e.g. an email address belonging to somebody else). However, it is the
  responsibility of the consumer to fill in these contact details correctly.
  Therefore this kind of identification disclosure is left out of
  consideration.
  \item Linkability and identiability are a threat for only a specific
  number of external dataflows, namely the one which involves interaction with a
  third party (i.e. billing service). The flow between UIS Communication
  Component and the UIS Web Service is not applicable for these theats
  because the contents of the flow are not personal. It is important to remark
  that the predictions will therefore not contain any pseudonymized consumption
  profiles. Demand predictions cannot be requested for a customer or group of
  customers but only for all customers or a large geographic region.  
  \item For all flows from and towards consumers and remote modules linkability
  and identiability threats do not apply. This is logical considering that
  unique identifiers are vital to contact both of these entities.

  %Processes.
  \item All internal processes are only susceptible to insider threats, as we
  consider the back-end sufficiently protected against outsider threats. All
  these processes will therefore be combined into a single process and only
  this process will be examined. 
  \item Linkability and identifiability are not considered as threats for
  processes because knowing that two actions belong to the same user does not
  violate that user's privacy. His or her privacy is only violated when the
  content of the action is revealed.
  \item Information Disclosure is still a threat that needs to be taken into
  account for processes as malicious insiders could still access the
  information.
  
  % Entities
  \item Identifiability and linkability of entities are no threat to the system
  as each of the entities has a unique identifier and there is no need to
  conceal this identity. 
  \item Content unawareness is only applicable to consumers as they are the only
  actors that enter actual (personal) data in the system. Other entities, like
  for example researchers only retrieve data from the system, the ReMeS
  personnel only retrieves statistics and registers new devices. Remote modules
  send measurements. The third party billing web service only registers whether
  bills are paid. Finally the UIS Communication component updates prices.
  Hence, all of these entities are not susceptible to the content unwareness
  threat.
\end{enumerate}

\subsection{Threats}
\label{sec:threats}

\input{threats/th01.tex}
\input{threats/th02.tex}
\input{threats/th03.tex}
\input{threats/th04.tex}
\input{threats/th05.tex}
\input{threats/th06.tex}
\input{threats/th07.tex}
\input{threats/th08.tex}
\input{threats/th09.tex}
\input{threats/th10.tex}
\input{threats/th11.tex}
