\chapter{Understanding the architecture}
\label{chap:understanding-architecture}

\npar All incoming communication goes through the Incoming Communication
Component. The received bits are, in the case of an alarm,  converted into an
alarm trame and are subsequently handed over to the right component. In this
case, it is the Alarm Processor. This is done through the Receive Alarm Trame
interface. The Alarm Processor will determine whether the remote module that
sent the alarm has a control valve associated with it (by retrieving the
configuration data from the Alarm Configuration Database). If so, the Actuator
Controller is invoked through its ActivateValve interface. Afterwards the alarm
will be stored in the measurements database (by constructing a query and
invoking the storeData(Query) method).

\npar The Actuator Controller will construct a command to shut down the
corresponding valve and invoke the Outgoing Communication Component’s
sendCommand() method. It is important that this command arrives at the remote
module so an acknowledgement is sent by the module upon receiving the
command. When the acknowledgement does not arrive within a certain interval, the
command is resent. If this happens several times in a row, a notification is
sent towards the customer to inform him of the multiple failures. The activation
of the valve is stored in the measurements and information database. All these
responsibilties belong to the Actuator Controller.

\npar Finally, an alarm notification is sent towards the customer (and/or
emergency services) by using the Outgoing Communication Component. In the
Outgoing Communication Component the different messages are sent according to
their priority. The command received from the Actuator Controller in this
case has a high priority. To notify all the stakeholders, the recipient
information is fetched from the database. The notification is also persisted.
