\section{CustomerProfileAPI}
\label{api:customer-profile-api}

\subsection{Interface Identity}

\npar \interface{CustomerProfileAPI} provides methods for the retrieval of and storage of
customer profile(s) (information).

\subsection{\method{execute(CustomerProfileQuery)}}

\subsubsection{Resources Provided}

\begin{quote}
	\begin{description}
		\item[Syntax] \
		\begin{verbatim}
CustomerProfileResult execute(CustomerProfileQuery query)
    throws IllegalQuerySyntaxException, NullPointerException;
		\end{verbatim}
		\item[Arguments] \
		\begin{itemize}
		  \item query: the query to be executed on the database. 
		\end{itemize}
		\item[Effect] The query is executed on the database and the result is returned
		as a CustomerProfileResult. 
		\item[Restrictions] \
		\begin{itemize}
		  \item The query can't be the null reference.
		  \item The syntax of the query has to be correct.
		\end{itemize}
	\end{description} 
\end{quote}

\subsubsection{Data Types Definition}

\begin{quote}
	\begin{description}
		\item[CustomerProfileResult] This object is a container for multiple
		CustomerProfiles.
		\item[CustomerProfileQuery] This object is a wrapper for queries only executable on a
		part of the shared repository, namely the customer profile storage.
		\item[CustomerProfile] This object is a container for all sorts of information useful
		for contacting a customer. This includes one or more alaram recipients, an
		adress, etc.
	\end{description} 
\end{quote}

\subsubsection{Exception Definition} 

\begin{quote}
	\begin{description}
		\item[NullPointerException] This exception is thrown when the given parameter
		is the null reference.
		\item[IllegalQuerySyntaxException] This exception is thrown when the syntax of
		the given query is invalid.
	\end{description} 
\end{quote}