\section{DeadlineStorageAPI}
\label{api:deadline-storage-api}

\subsection{Interface Identity}

\npar \interface{DeadlineStorageAPI} provides methods for the retrieval of and
storage of deadline(s) (information). By deadline we mean the expected arrival
time of the next trame of a remote module.

\subsection{\method{execute(DeadlineQuery)}}

\subsubsection{Resources Provided}

\begin{quote}
	\begin{description}
		\item[Syntax] \
		\begin{verbatim}
DeadlineResult execute(DeadlineQuery query)
    throws IllegalQuerySyntaxException, NullPointerException;
		\end{verbatim}
		\item[Arguments] \
		\begin{itemize}
		  \item query: the query to be executed on the database. 
		\end{itemize}
		\item[Effect] The query is executed on the database and the result is returned
		as a DeadlineResult. 
		\item[Restrictions] \
		\begin{itemize}
		  \item The query can't be the null reference.
		  \item The syntax of the query has to be correct.
		\end{itemize}
	\end{description} 
\end{quote}

\subsubsection{Data Types Definition}

\begin{quote}
	\begin{description}
		\item[DeadlineResult] This object is a container for one or more Deadlines. 
		\item[DeadlineQuery] This object is a wrapper for queries only executable on a
		part of the shared repository, namely the deadline storage.
		\item[Deadline] This object represents a deadline. This includes the next
		arrival time of a trame, an id number, possible delay, etc.
	\end{description} 
\end{quote}

\subsubsection{Exception Definition} 

\begin{quote}
	\begin{description}
		\item[NullPointerException] This exception is thrown when the given parameter
		is the null reference.
		\item[IllegalQuerySyntaxException] This exception is thrown when the syntax of
		the given query is invalid.
	\end{description} 
\end{quote}