\section{HealthMonitoringAPI}
\label{api:health-monitoring-unit-api}

\subsection{Interface Identity}

\npar The \interface{HealthMonitingAPI} interface provides methods for
receiving heartbeats of other components.

\subsection{\method{pulse(String, ComponentInfo)}}

\subsubsection{Resources Provided}

\begin{quote}
	\begin{description}
		\item[Syntax] \
		\begin{verbatim}
void pulse(String componentId, ComponentInfo info)
    throws NullPointerException, IllegalComponentIdException;
		\end{verbatim}
		\item[Arguments] \
		\begin{itemize}
		  \item componentId: is a unique identifier for a component in the system.
		  \item info: is an object with additional information concerning the
		  component. This information is optional.
		\end{itemize}
		\item[Effect] The heartbeat of the component with the given id is registered
		and the date and time for the latest heartbeat is also updated. Besides that,
		additional information can be processed (e.g. the storage component confirms
		it is alive but one of its replicas has failed).
		\item[Restrictions] \
		\begin{itemize}
		  \item The given id cannot must be valid.
		  \item The given id has to refer to an existing component.
		  \item A component can only call the \method{pulse()} method with its own
		  identifier as first argument. 
		\end{itemize}
	\end{description} 
\end{quote}

\subsubsection{Data Types Definition}

\begin{quote}
	\begin{description}
		\item[ComponentInfo] This object is a wrapper for additional information
		regarding the component that confirms it is alive. The information can for
		instance contain warnings about failing hardware that does not make the
		component fail. Think for instance about a failing disk in a RAID array.
	\end{description} 
\end{quote}

\subsubsection{Exception Definition} 

\begin{quote}
	\begin{description}
		\item[IllegalComponentIdException] This exception is thrown when the
		componentId doest not match the id number of any component in the system.
	\end{description} 
\end{quote}