\section{PredictionStorageAPI}
\label{api:prediction-storage-api}

\subsection{Interface Identity}

\npar \interface{PredictionStorageAPI} provides methods for the retrieval of and
storage of predictions.

\subsection{\method{execute(PredictionQuery)}}

\subsubsection{Resources Provided}

\begin{quote}
	\begin{description}
		\item[Syntax] \
		\begin{verbatim}
PredictionResult execute(PredictionQuery query)
    throws IllegalQuerySyntaxException, NullPointerException;
		\end{verbatim}
		\item[Arguments] \
		\begin{itemize}
		  \item query: the query to be executed on the database. 
		\end{itemize}
		\item[Effect] The query is executed on the database and the result is returned
		as a PredictionResult. 
		\item[Restrictions] \
		\begin{itemize}
		  \item The query can't be the null reference.
		  \item The syntax of the query has to be correct.
		\end{itemize}
	\end{description} 
\end{quote}

\subsubsection{Data Types Definition}

\begin{quote}
	\begin{description}
		\item[PredictionResult] This object is a container for multiple Predictions.
		\item[PredictionQuery] This object is a wrapper for queries only executable on
		a part of the shared repository, namely the prediction storage.
		\item[Prediction] This object is a container for all sorts of
		prediction information of how much of a certain utility to produce for
		a certain period. This object includes the predicted amount, the date,
		possible reasons why that this amount is what is it is, etc.
	\end{description} 
\end{quote}

\subsubsection{Exception Definition} 

\begin{quote}
	\begin{description}
		\item[NullPointerException] This exception is thrown when the given parameter
		is the null reference.
		\item[IllegalQuerySyntaxException] This exception is thrown when the syntax of
		the given query is invalid.
	\end{description} 
\end{quote}