\begin{description}
	\item[Primary actor] Customer
	\item[Interested parties] ReMeS, Utility providing company
	\item[Preconditions] \ 
	\begin{itemize}
		\item The customer is registered in the ReMeS system.
		\item The utility providing company has offered a lower price for consumers
		who are willing to send measurement data more frequently.
	\end{itemize}
	\item[Postconditions] \ 
	\begin{itemize}
		\item The remote monitoring module sends data more frequently
		\item The user has a lower utility price.
	\end{itemize}
	\item[Normal flow] \ 
	\begin{enumerate}
	  	% 1
	  	\item The user logs in to the ReMeS portal with his/her username and
	  	password.
	  	% 2
	  	\item The user navigates to the correct utility module for reconfiguration.
	  	% 3 
	  	\item There he/she selects that he/she is willing to send data more
	  	frequently inexchange for a lower utility price.
	  	% 4
	  	\item ReMeS receives this reconfiguration request and sends the
	  	corresponding command to the correct module.
	  	% 5
	  	\item The module receives this command and acknowledges it.
	\end{enumerate}
	\item[Alternate flow] \ 
	\begin{description}
		\item
	\end{description}
	\item[Exception flow] \ 
	\begin{description}
		\item[1a] Username and/or password are wrong.
		\begin{enumerate}
		  \item correct the spellingserrors(s) and retry.
		\end{enumerate}
		\item[4a] The request is lost.
		\begin{enumerate}
		  \item The user portal doesn't get an acknowledgement and has to resend the
		  request.
		\end{enumerate}
		\item[5a] The command is lost or not executed.
		\begin{enumerate}
		  \item The ReMeS system doesn't get an acknowledgement and has to resend the
		  command.
		 \end{enumerate}
	\end{description}
\end{description}