\begin{description}
	\item[Primary actor] ReMeS
	\item[Interested parties] Customer, Utilty providing company
	\item[Preconditions] \ 
	\begin{itemize}
		\item ReMeS has at least one operating monitoring module.
	\end{itemize}
	\item[Postconditions] \ 
	\begin{itemize}
		\item The utility control module closes the valve in case a leak is detected.
		\item ReMeS is aware of this profile for the control module.
	\end{itemize}
	\item[Normal flow] \ 
	\begin{enumerate}
	  	% 1
	  	\item The user logs in to the ReMeS portal with his/her username and
	  	password.
	  	% 2
	  	\item The user navigates to the correct utility control module for
	  	reconfiguration.
	  	% 3 
	  	\item There he/she selects the profile on how to act in case a leak is
	  	detected. In this case, he/she chooses to immediately close the valve in
	  	case of leak.
	  	% 4
	  	\item ReMeS receives this reconfiguration request and sends the
	  	corresponding to command to the correct control module.
	  	% 5
	  	\item The module receives this command and acknowledges it.
	\end{enumerate}
	\item[Alternate flow] \ 
	\begin{description}
		\item
	\end{description}
	\item[Exception flow] \ 
	\begin{description}
		\item[1a] Username and/or password are wrong.
		\begin{enumerate}
		  \item correct the spellingserrors(s) and retry.
		\end{enumerate}
		\item[4a] The request is lost.
		\begin{enumerate}
		  \item The user portal doesn't get an acknowledgement and has to resend the
		  request.
		\end{enumerate}
		\item[5a] The command is lost or not executed.
		\begin{enumerate}
		  \item The ReMeS system doesn't get an acknowledgement and has to resend the
		  command.
		 \end{enumerate}
	\end{description}
\end{description}