\begin{description}
	\item[Primary actor] Customer
	\item[Interested parties] ReMeS, Utility providing company, Third party payment
	service
	\item[Preconditions] \ 
	\begin{itemize}
		\item The customer has a pending invoice.
		\item The third party payment service has the invoice at it's disposal.
	\end{itemize}
	\item[Postconditions] \ 
	\begin{itemize}
		\item The customer has no more pending invoices and the invoice is paid.
		\item The utility providing company and third party payment service each got
		their share of the paid invoice.
	\end{itemize}
	\item[Normal flow] \ 
	\begin{enumerate}
	  	% 1
	  	\item The third party payment service notifies the customer that there is a
	  	pending invoice
	  	% 2
	  	\item The customer transfer the correct amount of money to the payment
	  	service before expiration of the due date.
	  	% 3 
	  	\item Upon receiving the correct amount of money from the customer, the
	  	payment service notifies ReMeS and the corresponding utility providing
	  	company.
	\end{enumerate}
	\item[Exception flow] \ 
	\begin{description}
		\item[2a] The customer pays not enough during the grace period
		\begin{enumerate}
		  \item The payment service discards the current invoice.
		  \item The payment service creates a new invoice containing the costs of the
		  previous invoice and additional costs for the reminder and interests.
		\end{enumerate}
		\item[2b] The customer pays too much
		\begin{enumerate}
		  \item The payment service returns the excess amount to the customer.
		\end{enumerate}
	\end{description}
\end{description}