\begin{description}
	\item[Source] Internal to the system
	\item[Stimulus] Hardware failure in the datacenter. Since the datacenter
	consists of several units, there could be various reasons for failure: one of
	the analysis, prediction, anomaly detection or storage servers goes down.
	\item[Artifact] All of the entities which make up the datacenter could be the
	artifact :
	\begin{enumerate}
	  \item Analysis unit
	  \item Prediction unit
	  \item Anomaly detection unit
	  \item Storage unit
	\end{enumerate}
	\item[Environment] During normal operation
	\item[Response] \
	\begin{enumerate}
	  \item Independent of the unit that goes down, the system should detect the
	  crash.
	  \item If the analysis or prediction unit goes down:
	  \begin{enumerate}
	    \item Any pending operations on the server should be cancelled and those
	    temporary results are lost (i.e. they have to be recalculated).
	    \item As long as the server is down, no new advices, predictions or alarms
	    can be made.
	    \item Under no circumstances can this failure leave (or bring) the system
	    in an inconsistent state.
	    \item A technician is dispatched to resolve the problem, this could be a
	    replacement of one single component or the whole server. The technician
	    could be belonging to ReMeS or the hardware manufacturer.
	    \item Upon resolving the problem, the server can resume his analysis,
	    prediction or anomaly detection tasks.
	  \end{enumerate}
	  \item If the storage unit goes down:
	  \begin{enumerate}
	   \item There should be at least one replica of all the data because ReMeS
	   core business (i.e. predicting, monitoring and analyzing) all relies on
	   (available) data.
	   \item Any pending operations on this (crashed) server should be cancelled
	   and resumed or restarted on the replica. In this way the rest of the system
	   has no knowledge of this recent crash.
	   \item Under no circumstances can this failure leave (or bring) the system
	    in an inconsistent state.
	    \item A technician is dispatched to resolve the problem, this could be a
	    replacement of one single component or the whole server. The technician
	    could be belonging to ReMeS or the hardware manufacturer.
	    \item When the main server is back up and running, the replica can return
	    control to the main server.
	  \end{enumerate}
	\end{enumerate}
	\item[Response measure] \
	\begin{enumerate}
	  \item The system has a guaranteed uptime of 99.9\% excluded from scheduled
	  maintenance.
	  \item In accordance to the SLA with the hardware manufacturer, the problem is
	  solved on time with respect to the SLA.
	\end{enumerate}
\end{description}